Approximating the Optimal State Abstraction

### 2016-05-01 icml_workshop/introduction.tex
adding rel work

% Planning and RL is hard.
For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,konidaris2007building,hauskrecht1998hierarchical,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}. Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.

>>>>

% Planning and RL is hard.
For this reason abstraction is of considerable interest in planning and \ac{RL} work~\yrcite{li2006towards,abelhershko2016approx,baird1995residual,sutton1999policy,mnih2015human,konidaris2007building,dietterich2000hierarchical,sacerdoti1974planning,hauskrecht1998hierarchical,anand2015novel,parr1998reinforcement,sutton1999between,konidaris2015constructing,Jiang2015,andre2002state}. Planning and \ac{RL} problems tackle solving for optimal behavior in \acp{MDP}.

### 2016-05-01 icml_workshop/related_work.tex
adding rel work

>>>>

\subsection{Abstraction as Function Approximation}

The use of function approximators for estimating the value function, model, or policy have seen extraordinary success in a variety of domains~\cite{mnih2015human,sutton1999policy,baird1995residual,stadie2015incentivizing,ormoneit2002kernel}. The use of such techniques achieves abstraction of a certain form - states that share some number of state variables receive similar signal from individual learning instances, thus generalizing knowledge far beyond an individual state. While some theoretical work has been done in this area~\cite{schoknecht2002optimality,thrun1993issues,parr2008analysis}, such analysis involves highly constraining assumptions (such as linearity or smoothness of the function class). Given that the goal of this work is to characterize effective abstractions by evaluating their relative satisfaction of each of our three desiderata, we stipulate that such analysis will prove illusive for these approaches.
